% !TEX root = ../main.tex
\chapter{Glossary}\label{glossary}
\begin{itemize}
\item \textbf{AXI}: Advanced eXtensible Interface, commonly used bus for transferring data in embedded devices and smart phones.

\item \textbf{MOPS}: Multiplicity Of Positive Steps, a trigger type in the UUB.

\item \textbf{PL}: Programmable Logic, this is the firmware and logic features running on the FPGA portion of the Zynq\textsuperscript{TM} chip.

\item \textbf{PPS, 1PPS}: Pulse per Second or One Pulse Per Second, usually refers to the GPS synchronized pulse put out by a time standard such as an atomic clock or GPS receiver.

\item \textbf{PS}: Processing System, this is the half of the Zynq\textsuperscript{TM} chip that hosts the operating system and functions as a system-on-a-chip.

\item \textbf{SBG}: Starburst Galaxy, a type of galaxy with a high star formation rate.

\item \textbf{SEP}: Spherical Error Probable, the radius from the mean of a collection of points within which 50\% of the points lie, used in GPS parlance.

\item \textbf{TOT}: Time Over Threshold, a type of trigger used in UHECR detectors.

\item \textbf{UB}: Unified Board, the original integrated electronic board for the Auger observatory, predecessor to the UUB.

\item \textbf{UUB}: Upgraded Unified Board, the board being fabricated for the AugerPrime upgrade. 

\item \textbf{UHECR}: Ultra High Energy Cosmic Ray, Cosmic rays with energies \textgreater 10$^{18}$ eV.

\item \textbf{UART}: Universal Asynchronous Transmitter/Receiver, the device which handles asynchronous communications, such as those for an RS-232 connection.

\item \textbf{VCXO}: Voltage Controlled Crystal Oscillator, and oscillator whose voltage is controlled by a changeable reference.
\end{itemize}

